Amphistomy increases leaf photosynthesis more in coastal than montane plants of Hawaiian ʻilima (\emph{Sida fallax})

### 2023-09-07 ms/ms.tex
ajb submission

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi

@@

Amphistomy increases photosynthesis in leaves of coastal ʻilima plants
more than that of montane plants. \(\mathrm{AA}\) was significantly
greater than 0 (95\% confidence intervals did not overlap 0) in 5 of 6
coastal leaves, but only 1 of 6 montane leaves
(\autoref{fig:habitat-aa}; see \autoref{fig:licor} for individual
curves). Overall, the average \(\mathrm{AA}\) among coastal and montane
leaves is \(0.12~[\numrange{0.077}{0.15}]\) and
\(0.027~[\numrange{-0.0044}{0.057}]\), respectively; the difference in
average \(\mathrm{AA}\) between habitat types is
\(\mathrm{AA}_\text{coastal} - \mathrm{AA}_\text{montane} = 0.089~[\numrange{0.04}{0.14}]\).
Posterior predictions closely match observed values of \(A\)
(\autoref{fig:pp-licor}), indicating an adequate model fit from which it
we can interpolate between measurements reliably. It also suggests that
slight extrapolation beyond the data should be reliable, but this is
less certain. When we remove two leaves where extrapolated slightly
beyond fitted \(A \textendash g_\mathrm{sw}\) curves, we estimate that
\(\mathrm{AA}_\text{coastal}\) is still positive,
\(0.081~[\numrange{0.022}{0.14}]\), but the difference between coastal
and montane leaves is smaller, \(0.053~[\numrange{-0.011}{0.12}]\), and
confidence intervals slightly overlap 0. Maximum photosynthetic rate was
slightly, but not significantly higher in coastal leaves (Welch Two
Sample \emph{t}-test, \(t_{9.65} = 1.6\), \(P = 0.14\)); total stomatal
conductance was similar (Welch Two Sample \emph{t}-test,
\(t_{9.71} = -0.09\), \(P = 0.93\)) in coastal and montane leaves
(\autoref{fig:habitat-Ags}).

>>>>

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, enhanced, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

Amphistomy increases photosynthesis in leaves of coastal ʻilima plants
more than that of montane plants. \(\mathrm{AA}\) was significantly
greater than 0 (95\% confidence intervals did not overlap 0) in 5 of 6
coastal leaves, but only 1 of 6 montane leaves
(\autoref{fig:habitat-aa}; see \autoref{fig:licor} for individual
curves). Overall, the average \(\mathrm{AA}\) among coastal and montane
leaves is \(0.12~[\numrange{0.077}{0.15}]\) and
\(0.027~[\numrange{-0.0044}{0.057}]\), respectively; the difference in
average \(\mathrm{AA}\) between habitat types is
\(\mathrm{AA}_\text{coastal} - \mathrm{AA}_\text{montane} = 0.089~[\numrange{0.04}{0.14}]\).
Posterior predictions closely match observed values of \(A\)
(\autoref{fig:pp-licor}), indicating an adequate model fit from which we
can interpolate between measurements reliably. It also suggests that
slight extrapolation beyond the data should be reliable, but this is
less certain. When we remove two leaves where extrapolated slightly
beyond fitted \(A \textendash g_\mathrm{sw}\) curves, we estimate that
\(\mathrm{AA}_\text{coastal}\) is still positive,
\(0.081~[\numrange{0.022}{0.14}]\), but the difference between coastal
and montane leaves is smaller, \(0.053~[\numrange{-0.011}{0.12}]\), and
confidence intervals slightly overlap 0. Maximum photosynthetic rate was
slightly, but not significantly higher in coastal leaves (Welch Two
Sample \emph{t}-test, \(t_{9.65} = 1.6\), \(P = 0.14\)); total stomatal
conductance was similar (Welch Two Sample \emph{t}-test,
\(t_{9.71} = -0.09\), \(P = 0.93\)) in coastal and montane leaves
(\autoref{fig:habitat-Ags}).

### 2023-09-07 ms/si.tex
ajb submission

\begin{document}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi

>>>>

\begin{document}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, interior hidden, enhanced, frame hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
